---
title       : Data Products
subtitle    : Orange Tree Growth Prediction 
author      : Louie Sakellaris
job         : Coursera Assignment
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Tree hugging is great
### Ever wanted to know how big that baby orange tree at the nursery will grow?  

### Now you can with this latest app.  

---

## How this app works



This app was developed using shinyapps and R's Orange data set.   
```{r}
data(Orange)
head(Orange)
``` 

---
## The prediction model

This app uses a mathematical model that can predict how big your orange tree will grow.  

```{r}
fit1<-lm(circumference~age,data=Orange)
summary(fit1)$call
summary(fit1)$coefficients
``` 

--- 

## Try it now

Try out the app at https://louieonshinyapps.shinyapps.io/orangeapp  

## Find out if Orange Trees are great hugging trees!
 ![alt text][id]
 [id]: orangetree.png
 